---
title: "INFLUENCE OF STRATEGIC MANAGEMENT ON PERFORMANCE OF HIV AND AIDS INTERVENTIONS MANAGED BY NON-GOVERNMENTAL ORGANISATIONS IN NYANZA REGION, KENYA"
author: "Leon Awiti"
date: "04/01/2021"
output: word_document
---

#Study Topic

#INFLUENCE OF STRATEGIC MANAGEMENT ON PERFORMANCE OF HIV AND AIDS INTERVENTIONS MANAGED BY NON-GOVERNMENTAL ORGANISATIONS IN NYANZA REGION, KENYA

#The study was guided by the following objectives: 

#1. To examine the influence of organisations purpose on performance of HIV and AIDS interventions managed by non-governmental organisations in Nyanza Region. 
#2. To establish the influence of environmental scanning on performance of HIV and AIDS interventions managed by non-governmental organisations in Nyanza Region. 
#3. To determine the influence of strategy formulation on performance of HIV and AIDS interventions managed by non-governmental organisations in Nyanza Region. 
#4. To assess the influence of strategy implementation on performance of HIV and AIDS interventions managed by non-governmental organisations in Nyanza Region. 
#5. To establish the influence of strategy evaluation and control on performance of HIV and AIDS interventions managed by non-governmental organisations in Nyanza Region. 
#6. To examine the moderating influence of stakeholder participation on the relationship between strategic management and performance of HIV and AIDS interventions managed by NGOs in Nyanza Region. 

#The study sought to test the following research hypotheses: 

#1. H0: There is no significant relationship between organizations purpose and performance of HIV and AIDS interventions managed by non-governmental organisations in Nyanza Region 
#2. H0: There is no significant relationship between environmental scanning and performance HIV and AIDS interventions managed by non-governmental organisations in Nyanza Region 
#3. H0: There is no significant relationship between strategy formulation and performance of HIV and AIDS interventions managed by non-governmental organisations in Nyanza Region 
#4. H0: There is no significant relationship between strategy implementation and performance of HIV and AIDS interventions managed by non-governmental organisations in Nyanza Region 
#5. H0: There is no significant relationship between strategy evaluation and control on performance of HIV and AIDS interventions managed by non-governmental organisations in Nyanza Region 
#6. H0: There is no significant moderating influence of stakeholder participation on the relationship between strategic management and performance of HIV and AIDS interventions managed by non-governmental organisations in Nyanza Region

```{r}
# Importing the dataset
Dataset <- read.csv("Strategic_Management.csv", header=TRUE)
```
```{r}
# Exploring the data
head(Dataset)
head(Dataset$Project_Perfomance)
```
```{r}
mean(Dataset$Project_Perfomance)
median(Dataset$Project_Perfomance)
```
```{r}
summary(Dataset)
summary(Dataset$Project_Perfomance)
```
```{r}
# Splitting the dataset into the Training set and Test set
# install.packages('caTools')
library(caTools)
set.seed(123)
split = sample.split(Dataset$Project_Perfomance, SplitRatio = 0.8)
training_set = subset(Dataset, split == TRUE)
test_set = subset(Dataset, split == FALSE)
```
```{r}
#correlations
cor(Dataset$Project_Perfomance, Dataset$OrganizationsPurpose)
cor(Dataset$Project_Perfomance, Dataset$EnvironmentalScanning)
cor(Dataset$Project_Perfomance, Dataset$StrategyFormulation)
cor(Dataset$Project_Perfomance, Dataset$StrategyImplementation)
cor(Dataset$Project_Perfomance, Dataset$StrategyEvaluation)
cor(Dataset$Project_Perfomance, Dataset$StakeholderParticipation)
```
```{r}
# Fitting Multiple Linear Regression to the Training set
regressor=lm("Project_Perfomance~OrganizationsPurpose+EnvironmentalScanning+StrategyFormulation + StrategyImplementation + StrategyEvaluation + StakeholderParticipation",data=training_set)
# Get summary of the model 
summary(regressor)
```
```{r}
# Get the coefficients
regressor$coefficients
```
```{r}
# Predicting the Test set results
y_pred = predict(regressor, newdata = test_set)
```
```{r}
# ANOVA table
anova(regressor)
```