---
title: "RELATIONSHIP BETWEEN WORKFORCE DIVERSITY AND EMPLOYEE PERFORMANCE IN PUBLIC UNIVERSITIES IN KENYA"
author: "Leon Awiti"
date: "11/01/2021"
output: word_document
---

#Study Topic
#RELATIONSHIP BETWEEN WORKFORCE DIVERSITY AND EMPLOYEE PERFORMANCE IN PUBLIC UNIVERSITIES IN KENYA

#The specific objectives:
#1.	To assess relationship between age diversity and employee performance in public universities in Kenya.
#2.	To establish relationship between gender diversity and employee performance in public universities in Kenya. 
#3.	To assess relationship between ethnic diversity and employee performance in public universities in Kenya.
#4.	To determine relationship between education background diversity and employee performance in public universities in Kenya.
#5.	To establish the moderating influence of organization culture on the relationship between workforce diversity and employee performance in public universities in Kenya.

#The study seeks to test the following hypotheses.
#H0. There is no significant relationship between gender diversity and employee performance in public universities in Kenya.
#H0. There is no significant relationship between age diversity and employee performance in public universities in Kenya. 
#H0. There is no significant relationship between ethnic diversity and employee performance in public universities in Kenya. 
#H0. There is no significant relationship between education background diversity and employee performance in public universities in Kenya.    
#H0. Organizational culture does not have a significant moderating influence on the relationship between workforce diversity and employee performance in public universities in Kenya.

```{r,echo=FALSE}
# Importing the dataset
Dataset <- read.csv("Workforce_Diversity.csv", header=TRUE)
```
```{r,echo=FALSE}
# Exploring the data
head(Dataset)
```
```{r,echo=FALSE}
summary(Dataset)
```
```{r,echo=FALSE}
# Splitting the dataset into the Training set and Test set
# install.packages('caTools')
library(caTools)
set.seed(120)
split = sample.split(Dataset$EmployeePerformance, SplitRatio = 0.8)
training_set = subset(Dataset, split == TRUE)
test_set = subset(Dataset, split == FALSE)
```
```{r,echo=FALSE}
#correlations
cor(Dataset$EmployeePerformance, Dataset$GenderDiversity)
cor(Dataset$EmployeePerformance, Dataset$AgeDiversity)
cor(Dataset$EmployeePerformance, Dataset$EthnicDiversity)
cor(Dataset$EmployeePerformance, Dataset$EducationDiversity)
cor(Dataset$EmployeePerformance, Dataset$OrganizationalCulture)
```
```{r,echo=FALSE}
# correlation matrix
dat <- Dataset[, c(0, 1:6)]
round(cor(dat), 2)
```
```{r,echo=FALSE}
# Fitting Multiple Linear Regression to the Training set

regressor=lm("EmployeePerformance~GenderDiversity+AgeDiversity+EthnicDiversity +EducationDiversity + OrganizationalCulture",data=training_set)

# Get summary of the model 
summary(regressor)
```
```{r,echo=FALSE}
# Get the coefficients
regressor$coefficients
```
```{r,echo=FALSE}
# Predicting the Test set results
y_pred = predict(regressor, newdata = test_set)
```
```{r,echo=FALSE}
# ANOVA table
anova(regressor)
```
