---
title: "STRATEGIC CAPABILITIES AND COMPETITIVE ADVANTAGE STUDY"
author: "Leon Awiti"
date: "11/01/2021"
output: word_document
---

# Study topic

#INFLUENCE OF STRATEGIC CAPABILITIES ON ON THE COMPETITIVE ADVANTAGE IN SUGAR COMPANIES IN WESTERN KENYA

# Study Objectives

#1.	To assess the influence of human resource capability on competitive advantage in sugar companies in Western Kenya.
#2.	To determine the influence of technology capability on competitive advantage in sugar companies in Western Kenya.
#3.	To establish the influence of material capability on competitive advantage in sugar companies in Western Kenya.
#4.	To assess the influence of financial resources capability on competitive advantage in sugar companies in Western Kenya.
#5.	To determine the moderating influence of Government regulatory policy on the relationship between strategic capabilities and competitive advantage in sugar companies in Western Kenya.

#Study Hypotheses

#1.	H0: There is no significant relationship between human resource capability and competitive advantage in sugar companies in Western Kenya.
#2.	H0: There is no significant relationship between technology capability and competitive advantage in sugar companies in Western Kenya.
#3.	H0: There is no significant relationship between material capability and competitive advantage in sugar companies in Western Kenya.
#4.	H0: There is no significant relationship between financial resources capability and competitive advantage in sugar companies in Western Kenya.
#5.	H0: The government regulatory policy does not moderate the relationship between strategic capabilities and competitive advantage in sugar companies in Western Kenya.
```{r}
# Importing the dataset
Dataset2 <- read.csv("Strategic_Capabilities.csv", header=TRUE)
```
```{r}
# Exploring the data
head(Dataset2)
```
```{r}
summary(Dataset2)
```
```{r}
# Splitting the dataset into the Training set and Test set
# install.packages('caTools')
library(caTools)
set.seed(120)
split = sample.split(Dataset2$CompetitiveAdvantage, SplitRatio = 0.8)
training_set = subset(Dataset2, split == TRUE)
test_set = subset(Dataset2, split == FALSE)
```
```{r}
#correlations
cor(Dataset2$CompetitiveAdvantage, Dataset2$HumanResourceCapability)
cor(Dataset2$CompetitiveAdvantage, Dataset2$TechnologyCapability)
cor(Dataset2$CompetitiveAdvantage, Dataset2$MaterialsCapability)
cor(Dataset2$CompetitiveAdvantage, Dataset2$FinancialCapability)
cor(Dataset2$CompetitiveAdvantage, Dataset2$GovernmentRegulation)
```
```{r}
# correlation matrix
dat <- Dataset2[, c(0, 1:6)]
round(cor(dat), 2)
```
```{r}
# Fitting Multiple Linear Regression to the Training set

regressor=lm("CompetitiveAdvantage~HumanResourceCapability+TechnologyCapability+MaterialsCapability + FinancialCapability + GovernmentRegulation",data=training_set)

# Get summary of the model 
summary(regressor)
```
```{r}
# Get the coefficients
regressor$coefficients
```
```{r}
# Predicting the Test set results
y_pred = predict(regressor, newdata = test_set)
```
```{r}
# ANOVA table
anova(regressor)
```
