---
title: "STAKEHOLDER PARTICIPATION ON SUSTAINABILITY OF COMMUNITY DEVELOPMENT PROJECTS"
author: "Leon Awiti"
date: "11/01/2021"
output: word_document
---

#Study Topic

#Influence of Stakeholder Participation on Sustainability of Community Development Projects Implemented by Plan International in Homa Bay Town Sub-County, Kenya

#The Specific Objectives

#i) To determine the influence of passive participation among stakeholders on sustainability of community development projects implemented by Plan International in Homa Bay Town Sub-County
#ii) To examine the influence of interactive participation among stakeholders on sustainability of community development projects implemented by Plan International in Homa Bay Town Sub-County
#iii) To establish the influence of functional participation among stakeholders on sustainability of community development projects implemented by Plan International in Homa Bay Town Sub-County
#iv) To investigate the influence of optimum participation among stakeholders on sustainability of community development projects implemented by Plan International in Homa Bay Town Sub-County

#Study Hypotheses

#i) There is no significant relationship between passive participation among stakeholders and sustainability of community development projects implemented by Plan International in Homa Bay Town Sub-County
#ii) There is no significant relationship between interactive participation among stakeholders and sustainability of community development projects implemented by Plan International in Homa Bay Town Sub-County
#iii) There is no significant relationship between functional participation among stakeholders and sustainability of community development projects implemented by Plan International in Homa Bay Town Sub-County
#iv) There is no significant relationship between optimum participation among stakeholders on sustainability of community development projects implemented by Plan International in Homa Bay Town Sub-County
```{r}
# Importing the dataset
Dataset4 <- read.csv("StakeholderParticipation.csv", header=TRUE)
```
```{r}
# Exploring the data
head(Dataset4)
```
```{r}
summary(Dataset)
```
# Splitting the dataset into the Training set and Test set
# install.packages('caTools')
library(caTools)
set.seed(120)
split = sample.split(Dataset4$ProjectSustainability, SplitRatio = 0.8)
training_set = subset(Dataset4, split == TRUE)
test_set = subset(Dataset4, split == FALSE)

```{r}
#correlations
cor(Dataset4$ProjectSustainability, Dataset4$PassiveParticipation)
cor(Dataset4$ProjectSustainability, Dataset4$InteractiveParticipation)
cor(Dataset4$ProjectSustainability, Dataset4$FunctionalParticipation)
cor(Dataset4$ProjectSustainability, Dataset4$OptimalParticipation)
```
```{r}
# correlation matrix
dat <- Dataset4[, c(0, 1:5)]
round(cor(dat), 2)
```
```{r}
# Fitting Multiple Linear Regression to the Training set
regressor=lm("ProjectSustainability~PassiveParticipation+InteractiveParticipation+FunctionalParticipation +OptimalParticipation",data=training_set)

# Get summary of the model 
summary(regressor)
```
```{r}
# Get the coefficients
regressor$coefficients
```
```{r}
# Predicting the Test set results
y_pred = predict(regressor, newdata = test_set)
```
```{r}
# ANOVA table
anova(regressor)
```