---
title: INFLUENCE OF STRATEGY IMPLEMENTATION DRIVERS ON WATER SERVICE DELIVERY IN LAKE
  VICTORIA SOUTH REGION, KENYA
author: "Leon Awiti"
date: "11/01/2021"
output: word_document
---

#Topic of the study 

#INFLUENCE OF STRATEGY IMPLEMENTATION DRIVERS ON WATER SERVICE DELIVERY IN LAKE VICTORIA SOUTH REGION, KENYA

#Objectives of the study 

#i).To examine the influence of organizational structure on water service delivery in Lake Victoria south region, Kenya. 
#ii).To establish the influence of human capital development on water service delivery in Lake Victoria south region, Kenya. 
#iii).To determine the influence of corporate governance practices on water service delivery in Lake Victoria south region, Kenya. 
#iv).To assess the influence of technological adoption on water service delivery in Lake Victoria south region, Kenya. 
#v).To determine the moderating effect of government regulatory policies on the relationship between strategy implementation drivers and water service delivery in Lake Victoria south region. 

#Study Hypotheses

#i)H0 Organizational structure has no significant influence on water service delivery in Lake Victoria south region, Kenya.
#ii)H0 Human capital  development has no significant influence on water service delivery in Lake Victoria south region, Kenya.
#iii)H0 Corporate governance practices have no significant influence on water service delivery in Lake Victoria south region, Kenya.
#iv)H0 There is no significant relationship between the technological adoption and water service delivery in Lake Victoria south region, Kenya.
#v)H0 There is no significant moderating effect of government regulatory policies on the relationship between strategy implementation drivers and water service delivery.
```{r}
# Importing the data
Dataset7 <-read.csv("WaterServiceDelivery.csv",header=TRUE)
```
```{r}
# Exploring the data
head(Dataset7)
```
```{r}
summary(Dataset7)
```
# Splitting the dataset into the Training set and Test set
# install.packages('caTools')
library(caTools)
set.seed(123)
split = sample.split(Dataset7, SplitRatio = 0.8)
training_set = subset(Dataset7, split == TRUE)
test_set = subset(Dataset7, split == FALSE)

```{r}
#correlations
cor(Dataset7$WaterServiceDelivery, Dataset7$TechnologyAdoption)
cor(Dataset7$WaterServiceDelivery, Dataset7$CorporateGovernancePractices)
cor(Dataset7$WaterServiceDelivery, Dataset7$OrganizationalStructure)
cor(Dataset7$WaterServiceDelivery, Dataset7$HumanCapitalDevelopment)
cor(Dataset7$WaterServiceDelivery, Dataset7$GovernmentRegulatoryPolicies)
```
```{r}
# correlation matrix
dat <- Dataset7[, c(0, 1:6)]
round(cor(dat), 2)
```
```{r}
# Fitting Multiple Linear Regression to the Training set
regressor=lm("WaterServiceDelivery~TechnologyAdoption+CorporateGovernancePractices+OrganizationalStructure+HumanCapitalDevelopment+GovernmentRegulatoryPolicies",data=training_set)

# Get summary of the model 
summary(regressor)
```
```{r}
# Get the coefficients
regressor$coefficients
```
```{r}
# Predicting the Test set results
y_pred = predict(regressor, newdata = test_set)
```
```{r}
# ANOVA table
anova(regressor)
```
